Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-17 intro.tex
added a pageref label to intro.tex

The information in an observation can be partitioned into two pieces:
redundancy and entropy generation\cite{crutchfield2003}.  Our approach
exploits this decomposition in order to assess how much predictive
structure is present in a signal---i.e., where it falls on the
complexity spectrum mentioned above.  We define \emph{complexity} as a
particular approximation of Kolmogorov-Sinai entropy\cite{KS-entropy}.
That is, we view a random-walk time series (which exhibits high
entropy) as purely complex, whereas a periodic signal, which exhibits
low entropy, is on the low end of the complexity spectrum.  We argue
that an extension of \emph{permutation entropy}
\cite{bandt2002per}---a method for approximating the entropy through
ordinal analysis---is an effective way to assess the complexity of a
given time series.  Permutation entropy is ideal for our purposes
because it works with real-valued data and is known to converge to the true entropy value. Other
existing techniques either require specific knowledge of the
generating process or produce biased values of the
entropy~\cite{bollt2001}.

>>>>

The information in an observation can be partitioned into two pieces:
redundancy and entropy generation\cite{crutchfield2003}.  
\label{page:redundancy}
Our approach
exploits this decomposition in order to assess how much predictive
structure is present in a signal---i.e., where it falls on the
complexity spectrum mentioned above.  We define \emph{complexity} as a
particular approximation of Kolmogorov-Sinai entropy\cite{KS-entropy}.
That is, we view a random-walk time series (which exhibits high
entropy) as purely complex, whereas a periodic signal, which exhibits
low entropy, is on the low end of the complexity spectrum.  We argue
that an extension of \emph{permutation entropy}
\cite{bandt2002per}---a method for approximating the entropy through
ordinal analysis---is an effective way to assess the complexity of a
given time series.  Permutation entropy is ideal for our purposes
because it works with real-valued data and is known to converge to the true entropy value. Other
existing techniques either require specific knowledge of the
generating process or produce biased values of the
entropy~\cite{bollt2001}.
